Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-24 ind_files/06_nontechnical_discussion.tex
Slightly resize table

{\centering\begin{sideways}
		\begin{minipage}{\textheight}
			\resizebox{\textheight}{!}{%
				\setstretch{1.5}
				\begin{tabular}{ %I manually specified the width of each column by trial and error
						|p{\dimexpr.25\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 1
						|p{\dimexpr.27\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 2
						|p{\dimexpr.33\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 3
						|p{\dimexpr.25\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 4
						|p{\dimexpr.4\linewidth-2\tabcolsep-1.3333\arrayrulewidth}|% column 5
					}
					\hline
					\centering \textbf{Number of possible distinct types/trait variants ($m$)} & \centering \textbf{State Space} &
					\centering \textbf{Model parameters} & \centering \textbf{Mesoscopic description} & \centering\arraybackslash \textbf{Infinite population limit} \\
					\hline
					$m = 1$ \newline (Identical individuals)  & $[0,1,2,3,\ldots]$ \newline (Population size) & Two non-negative functions, $b(n)$ and $d(n)$, describing the birth and death rate of individuals when the population size is $n$ & Univariate Fokker-Planck equation \newline (one-dimensional SDEs) & Dynamics of populations of identical individuals\\ 
					\hline
					$1 < m < \infty$ \newline (Discrete traits) & $[0,1,2,3,\ldots]^{m}$ \newline (Number of individuals of each trait variant) & $2m$ non-negative functions, $b_i(\mathbf{n})$ and $d_i(\mathbf{n})$ (for $1 \leq i \leq m$) describing the birth and death rate of trait variant $i$ when the population is $\mathbf{n}=[n_1,\ldots,n_m]$ & Multivariate Fokker-Planck equation \newline ($m$-dimensional SDEs) &  Evolutionary game theory \newline
					Lotka-Volterra competition \newline Quasispecies equation \newline Price equation (discrete traits) \\
					\hline
					$m = \infty$ \newline (Quantitative traits) & $ \left\{\sum\limits_{i=1}^{n}\delta_{x_i} \ \bigg{|} \ n \in \mathbb{N}, \ x_i \in \mathcal{T} \subseteq \mathbb{R}\right\}$ \newline \newline (Each Dirac mass $\delta_{x_i}$ is an individual with trait value $x_i$ in the trait space $\mathcal{T}$) & Two non-negative functionals $b(x|\nu)$ and $d(x|\nu)$ describing the birth and death rate of trait variant $x$ when the population is the (stochastic) field/function $\nu$ & Functional Fokker-Planck equation/Field theory \newline (SPDEs) & Kimura's continuum-of-alleles model \newline~\posscite{sasaki_oligomorphic_2011} Oligomorphic Dynamics \newline~\posscite{wickman_theoretical_2022} Trait Space Equations for intraspecific trait variation \newline Gradient Dynamics \newline Price equation (quantitative traits)\\
					\hline
				\end{tabular}
			}
			%\renewcommand\thetable{1}
			\captionof{table}{Summary of the various birth-death processes studied in this thesis}
			\label{table_summary}
		\end{minipage}
	\end{sideways}\par}
\clearpage

>>>>

{\centering\begin{sideways}
		\begin{minipage}{\textheight}
			\resizebox{\textheight}{!}{%
				\setstretch{1.5}
				\begin{tabular}{ %I manually specified the width of each column by trial and error
						|p{\dimexpr.25\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 1
						|p{\dimexpr.29\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 2
						|p{\dimexpr.33\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 3
						|p{\dimexpr.25\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 4
						|p{\dimexpr.4\linewidth-2\tabcolsep-1.3333\arrayrulewidth}|% column 5
					}
					\hline
					\centering \textbf{Number of possible distinct types/trait variants ($m$)} & \centering \textbf{State Space} &
					\centering \textbf{Model parameters} & \centering \textbf{Mesoscopic description} & \centering\arraybackslash \textbf{Infinite population limit} \\
					\hline
					$m = 1$ \newline (Identical individuals)  & $[0,1,2,3,\ldots]$ \newline (Population size) & Two non-negative functions, $b(n)$ and $d(n)$, describing the birth and death rate of individuals when the population size is $n$ & Univariate Fokker-Planck equation \newline (one-dimensional SDEs) & Dynamics of populations of identical individuals\\ 
					\hline
					$1 < m < \infty$ \newline (Discrete traits) & $[0,1,2,3,\ldots]^{m}$ \newline (Number of individuals of each trait variant) & $2m$ non-negative functions, $b_i(\mathbf{n})$ and $d_i(\mathbf{n})$ (for $1 \leq i \leq m$) describing the birth and death rate of trait variant $i$ when the population is $\mathbf{n}=[n_1,\ldots,n_m]$ & Multivariate Fokker-Planck equation \newline ($m$-dimensional SDEs) &  Evolutionary game theory \newline
					Lotka-Volterra competition \newline Quasispecies equation \newline Price equation (discrete traits) \\
					\hline
					$m = \infty$ \newline (Quantitative traits) & $ \left\{\sum\limits_{i=1}^{n}\delta_{x_i} \ \bigg{|} \ n \in \mathbb{N}, \ x_i \in \mathcal{T} \subseteq \mathbb{R}\right\}$ \newline \newline (Each Dirac mass $\delta_{x_i}$ is an individual with trait value $x_i$ in the trait space $\mathcal{T}$) & Two non-negative functionals $b(x|\nu)$ and $d(x|\nu)$ describing the birth and death rate of trait variant $x$ when the population is the (stochastic) field/function $\nu$ & Functional Fokker-Planck equation/Field theory \newline (SPDEs) & Kimura's continuum-of-alleles model \newline~\posscite{sasaki_oligomorphic_2011} Oligomorphic Dynamics \newline~\posscite{wickman_theoretical_2022} Trait Space Equations for intraspecific trait variation \newline Gradient Dynamics \newline Price equation (quantitative traits)\\
					\hline
				\end{tabular}
			}
			%\renewcommand\thetable{1}
			\captionof{table}{Summary of the various birth-death processes studied in this thesis}
			\label{table_summary}
		\end{minipage}
	\end{sideways}\par}
\clearpage
